\documentclass[phd,tocprelim]{thesis}
%% Added to avoid the \ifpdf name clash error
\let\ifpdf\relax
%
% tocprelim option must be included to put the roman numeral pages in the
% table of contents
%
% The cornellheadings option will make headings completely consistent with
% guidelines.
%
% This sample document was originally provided by Blake Jacquot, and
% fixed up by Andrew Myers.
%
%Some possible packages to include
\usepackage{graphicx,pstricks}
\usepackage{graphics}
\usepackage{moreverb}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{hangcaption}
\usepackage{txfonts}
\usepackage{palatino}
\usepackage[graphicx]{realboxes}


\usepackage{graphicx}
\usepackage{import}
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{xfrac}
\usepackage{tabu}
\usepackage{color}
\usepackage{cite}
\usepackage{array}
\usepackage{listings}
\usepackage{parskip}
\usepackage{nicefrac}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{tocloft}
\usepackage{float}
\usepackage{array}
\usepackage{subfig}
\usepackage{gensymb}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{pdfpages}
\usepackage{url}

\usepackage[pdftex]{graphicx}
\usepackage{float}
\usepackage{booktabs,caption,fixltx2e}

%todo:
\usepackage{todonotes}


%if you're having problems with overfull boxes, you may need to increase
%the tolerance to 9999
\tolerance=9999

\bibliographystyle{plain}
%\bibliographystyle{IEEEbib}

\renewcommand{\caption}[1]{\singlespacing\hangcaption{#1}\normalspacing}
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.75}

\title {Mapping and Classification of Microorganism}
\author {Emilie M Hyrum Dahl}
\conferraldate {December}{2018}
\degreefield {MSc}
\copyrightholder{Emilie M Hyrum Dahl}
\copyrightyear{2018}

\begin{document}
%Veldig viktig med konsistens i table of contents. Feks kan vi ha sånn at alle forbokstaver på alle ord er stor..

\maketitle
\makecopyright

\begin{abstract}
The ocean plays a great part in life on earth, not only as a source to oxygen and food for living beings, but also as a vital influence to the climate and weather. The ocean, with all that comes with it, is simply a necessity for life on earth. Nevertheless, this same ocean is not taken care of. Millions of pieces of plastics, especially micro-plastic, pollutes and eradicate sea life every day, indirectly affecting life on land. 
\\\\
The road to a clean sea can be divided into steps. First step is to prevent the continuous supply of trash and plastic pollution. The next step should involve picking up what is already in the ocean. The latter action is further divided into sub-steps. As ocean is huge, attacking all parts of the sea is next to impossible. Being able to map and monitor the ocean columns and determine critical areas is thus a good start. Therefore, this thesis will concern methods for detection and analyzing micro-plastics. 

%An abstract is a brief summary of a research article, thesis, review, conference proceeding, or any in-depth analysis of a particular subject and is often used to help the reader quickly ascertain the paper's purpose.
\end{abstract}

\begin{preface}
This thesis is submitted in partial fulfillment of the requirements for the degree of master of science (MSc) at the Norwegian University of Science and Technology (NTNU). The main work is conducted at Department of Marine Technology, NTNU, while part of the work has been conducted at the Department of Biology, NTNU in cooperation with Aksel Mogstad. 
\\\\
I have cooperated with Andreas Stien in large part. Next to all testing and work done hands on, have been done together with Andreas. Therefore we share the same approach and results. 

\todo[inline]{burde man her si at ettersom dette i utgangspunktet er et litteraturstudie, er background- og theory-seksjonen forsøkt mer elaborated enn resultatdelen etc}

\end{preface}

\begin{acknowledgements}
This project thesis and final report has been supported by members of the faculty at NTNU. The author of this report would particularly like to thank supervisor Professor Asgeir J. Sørensen at IMT NTNU and PhD. candidate Aksel Mogstad, who have been at close guidance throughout this project and the entire semester. 
\\\\
In addition, a great thanks should be directed towards Professor Geir Johnsen at the Department of Biology NTNU, who provided insight and expertise that greatly assisted the project and thereby this report.
\end{acknowledgements}

\begin{summary}
Your summary goes here. Make sure it sits inside
the brackets.
\end{summary}

\contentspage
\tablelistpage
\figurelistpage

\normalspacing \setcounter{page}{1} \pagenumbering{arabic}
\pagestyle{thesis} \addtolength{\parskip}{0.5\baselineskip}

\chapter{Introduction}
\input{Chapters/Introduction.tex}

\chapter{The Problem}
\input{Chapters/Problem.tex}

\chapter{Theory}
\input{Chapters/Theory.tex}

\chapter{{Approach/Method}}
\input{Chapters/Method.tex}

\chapter{Results}
\input{Chapters/Results.tex}

\chapter{Discussion}
\input{Chapters/Discussion.tex}

\chapter{Conclusion and Recommendation for Further Work}
\input{Chapters/Conclution.tex}


\appendix
\chapter{Chapter 1 of appendix}
Appendix chapter 1 text goes here

\bibliography{sampleThesis}

\end{document}